Supporting Information for\\ ``A weakly structured stem for human origins in Africa''

### 2022-08-12 supplement.tex
finalized discussion of TSI

Across all validations to alternative datasets described in this section, model
fits were largely robust and matched those shown in the main text
(Figure~\ref{fig:best-fit-models})---the single outlier in these validations
was the continuous migration model fit to the dataset that included TSI instead
of GBR. We conclude that while there remain important issues

Together, this highlights the sensitivity of
complex demographic inference to the choices of populations to include, as well
as to choices of model specification.
\aprcomment{not sure about these last two sentences}

>>>>

In summary, across all validations to alternative datasets described in this section, model
fits were largely robust and matched those shown in the main text
(Figure~\ref{fig:best-fit-models})---the single outlier in these validations
was the estimated divergence time for the Nama in the continuous migration model
fit to the dataset that included TSI instead of GBR.  
Thus, while specific aspects of the inferred demographic inference can be sensitive
to the choices of populations to include and the choices of model specification, 
the results presented in the main text are broadly robust to choices of model, dataset, and 
analysis choices. 
Our conclusions in the main text took into account both this overall robustness 
and the important sources of uncertainty.
